Efficient Planning for Sokoban with Answer Set Programming - A Case Study

### 2018-07-28 BATexFiles/Draft.tex
Refined some wordings in the Tex, tried around with the plain-f+c-split encoding to get it to order lexicographically

\title{Title}

@@

Sokoban approach with ASP planning -$>$ Plain, Inc, Optimization (?)

@@

What do i do? I'm working on the Sokoban problem and trying to do my best to find a fast and easy solution to it. I'm not working on any level but just the ones meeting some criteria. I'm picking qualitative and quantitative characteristics and deciding on some values to examine. My encodings are supposed to work better on some of the instances and worse on others. What rules describe those fluctuations? Is there a trend when comparing runtimes to my qualitative and quantitative characteristics? E.g. you would expect the runtime to go up when the instance's size grows or when the amount of boxes in the level grows.
In this thesis I will work on optimizing ASP encodings for the game Sokoban towards different instances.

@@

The first try to construct a naive encoding to solve sokoban-instances yielded a solution that works in a common way in ASP planning. In line 4 we initialize the information from the level instance with the time 0. In line 7 we state the there is one move at minimum and at maximum for each timestep. This makes the ASP planner guess the sequence of moves and infer every successive state from the moves it picks. In lines 9-13 we calculate the successor state from the move picked in line 7. Line 9 calculates the new player-position, line 11 calculates the new position of the box in the players way and line 13 calculates the new position of boxes not touched by the player. Additionally we need some integrity constraints to prevent illegal states. The integrity constraint in line 15 ensures that at no time a box or player has a position outside of the playing field. The integrity constraint in line 17 ensures that at no time boxes or the player share one field.

@@

\subsection{Incremental Encoding}
\lstinputlisting{../Encodings/SokobanPlainEncodingInc.lp}
The incremental encoding is similar to the plain encoding. The difference is the partition of the encoding into three parts: the \#program base in lines 3-5 which is independent of the step parameter t, the \#program step in lines 7-19 which is the cumulative part, collecting knowledge and the \#program check in lines 21-25 which is specific for each value of t. This allows for gradually processing each time step and accumulating knowledge that persists even if the current step is not satisfiable.
\subsection{Advanced Encoding}
\lstinputlisting{../Encodings/SokobanPlainEncodingOpti.lp}
\section{Evaluation}
\section{Experiments and Results}
\chapter{Discussion of Results}
compare chapter State of the Art with chapter My Work \cite{LifschitzASP}

>>>>

\title{Efficient Planning for Sokoban with Answer Set Programming - A Case Study}

@@

Sokoban approach with ASP planning $\rightarrow$ PlainEnc, IncEnc, Optimization (?)

@@

What do i do? I'm working on the Sokoban problem and trying to do my best to find a fast and easy solution to it. I'm not working on any level but just the ones meeting some criteria. I'm picking qualitative and quantitative characteristics and deciding on some values to examine. My encodings are supposed to work better on some of the instances and worse on others. What rules describe those fluctuations? What assumptions can be made? Is there a trend when comparing runtimes to my qualitative and quantitative characteristics? E.g. you would expect the runtime to go up when the instance's size grows or when the amount of boxes in the level grows.
In this thesis I will work on optimizing ASP encodings for the game Sokoban towards different instances. First Ill briefly explain what Sokoban is and how it is played, then Ill give a short introduction on comparable/similar/other scientific studies concerning sokoban. Then Ill go over my work, ... and finally evaluation and Discussion of Results.

@@

The first try to construct a naive encoding to solve sokoban-instances yielded a solution that works in a common way in ASP planning. In line 4 we initialize the information from the level instance with the time 0. In line 7 we state that there is one move at minimum and at maximum for each timestep. This makes the ASP planner ground all sequences of moves, pick one for every timestep and infer every successive state from the moves it picks. In lines 9-13 we calculate the successor state from the move picked in line 7. Line 9 calculates the new player-position, line 11 calculates the new position of the box in the players way and line 13 calculates the new position of boxes not touched by the player. Additionally we need some integrity constraints to prevent illegal states. The integrity constraint in line 15 ensures that at no time a box or player has a position outside of the playing field. The integrity constraint in line 17 ensures that at no time boxes or the player share one field.

@@

\subsection{Incremental Encoding}
\lstinputlisting{../Encodings/SokobanPlainEncodingInc.lp}
The incremental encoding is similar to the plain encoding. The difference is the partition of the encoding into three parts: the \#program base in lines 3-5 which is independent of the step parameter t, the \#program step in lines 7-19 which is the cumulative part, collecting knowledge and the \#program check in lines 21-25 which is specific for each value of t (STEP ALSO IS THOUGH). This allows for gradually processing each time step and accumulating knowledge that persists even if the current step is not satisfiable.

\subsection{Advanced Encoding}
\lstinputlisting{../Encodings/SokobanPlainEncodingOpti.lp}
\section{Evaluation}
\section{Experiments and Results}
\chapter{Discussion of Results}
compare chapter State of the Art with chapter My Work \cite{LifschitzASP}
